MAESTROeX: A Massively Parallel Low Mach Number Astrophysical Solver

### 2019-06-04 MAESTROeX_I/intro.tex

In this paper, we present new algorithmic methodology that improves upon Paper V in a number of ways.
First, the overall temporal algorithm has been greatly simplified without compromising accuracy.
The key design decisions were to eliminate the splitting of the velocity into average and perturbational components, 
and also to replace the hydrodynamic evolution of the base state with a predictor-corrector approach.
Not only does this greatly simplify the dynamics of the base
state, but this treatment is more amenable to higher-order multiphysics coupling strategies
based on method-of-lines integration.  
In particular, schemes based on spectral deferred corrections have been used to generate high-order temporal integrators for problems of reactive flow \citep{dutt2000spectral} and low Mach number combustion \citep{pazner2016high,nonaka2018conservative}.
Second, we explore the effects of alternative spatial mapping routines for coupling the base state and the Cartesian grid state in spherical problems.
Finally, the code has been completely ported to a new software framework suitable for modern manycore and GPU-based supercomputers.
We examine the performance of our new MAESTROeX implementation in the new C++/F90 AMReX public software library \cite{AMReX,AMReX_JOSS}.
MAESTROeX uses MPI+OpenMP parallelism and scales well to over 10,000 MPI processes, with each MPI process supporting tens of threads.
The resulting code is publicly available on GitHub ({\tt https://github.com/AMReX-Astro/MAESTROeX}),
uses the Starkiller-Astro microphysics libraries ({\tt https://github.com/starkiller-astro/Microphysics}),
and the AMReX software library for block-structured adaptive mesh refinement ({\tt https://github.com/AMReX-Codes/amrex}).

>>>>

In this paper, we present new algorithmic methodology that improves upon Paper V in a number of ways.
First, the overall temporal algorithm has been greatly simplified without compromising accuracy.
The key design decisions were to eliminate the splitting of the velocity into average and perturbational components, 
and also to replace the hydrodynamic evolution of the base state with a predictor-corrector approach.
Not only does this greatly simplify the dynamics of the base
state, but this treatment is more amenable to higher-order multiphysics coupling strategies
based on method-of-lines integration.  
In particular, schemes based on spectral deferred corrections have been used to generate high-order temporal integrators for problems of reactive flow \citep{dutt2000spectral} and low Mach number combustion \citep{pazner2016high,nonaka2018conservative}.
Second, we explore the effects of alternative spatial mapping routines for coupling the base state and the Cartesian grid state in spherical problems.
Finally, the code has been completely ported to a new software framework suitable for modern manycore and GPU-based supercomputers.
We examine the performance of our new MAESTROeX implementation in the new C++/F90 AMReX public software library \citep{AMReX,AMReX_JOSS}.
MAESTROeX uses MPI+OpenMP parallelism and scales well to over 10,000 MPI processes, with each MPI process supporting tens of threads.
The resulting code is publicly available on GitHub ({\tt https://github.com/AMReX-Astro/MAESTROeX}),
uses the Starkiller-Astro microphysics libraries \citep{starkiller},
and the AMReX software library for block-structured adaptive mesh refinement ({\tt https://github.com/AMReX-Codes/amrex}).
